---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CAGErAid

<!-- badges: start -->
<!-- badges: end -->

The goal of CAGErAid is to assist in using [CAGEr](https://rdrr.io/bioc/CAGEr/) for analysis of CAGE data for cross-alignments between Barcelona, Osaka and Okinawa samples of Oikopleura dioica, with and without splice leader sequences.

## Installation

You can install the development version of CAGErAid from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
devtools::install_github('a-klarkowska/CAGErAid') |> suppressPackageStartupMessages()

```

## Polishing data

After cross-aligning CAGE reads to the Barcelona, Osaka and Okinawa genomes, we can use [`getCTSS()`](https://rdrr.io/bioc/CAGEr/man/getCTSS.html) on a CAGEexp object. For details on how to load the data, see [this vignette](vignettes/loading_polishing.Rmd). 

```{r example, message=FALSE}
library(CAGErAid) |> suppressPackageStartupMessages()

# load CAGEexp object - Barcelona reads aligned to Barcelona genome
ce_path <- system.file("extdata", "ce_clean.rds", package="CAGErAid")
ce <- readRDS(ce_path)

```

The CAGEexp file could use some polishing on the sample names and a little more information on the samples themselves. To do that, we can use `quickPolish()`. To add metadata from the nf-core RNAseq pipeline QC, we call `quickMQC()`.

```{r polishing}
ce <- ce |> 
  quickPolish() |> 
  quickMQC()

```

To easily annotate data, we can use `quickGFF()`.

```{r annotation}
gff_path <- system.file('extdata', 'Barcelona.gtf', package = 'CAGErAid')
gff <- quickGFF(gff_path, types = c('transcript', 'exon'))
ce <- CAGEr::annotateCTSS(ce, gff)

```

For more details on the cross-alignments analysis workflow, consult the vignettes on [loading](vignettes/loading.Rmd) the data, [polishing it and basic stats analysis](vignettes/polishing.Rmd), and clustering of [SL-containing samples](vignettes/clustering_sl.Rmd) and [samples without SL](vignettes/clustering_no.Rmd).
